---
title: "Programming Background"
author: "Allison Warhus"
date: "9/11/2021"
---

```{r}
knitr::opts_chunk$set(fig.path = "../images/")
```

## Programming Background Blog Post

I prefer R over all other programs I have learned. I find it significantly more intuitive and less convoluted than other programs. I like that R is open source, so there are a lot of different packages to help you achieve whatever it is you are trying to do. I also like how much documentation there is available about those packages online.
I don't miss anything about other languages. I do like like programming except in R. I do not consider R difficult to learn at all. At worst it is tedious, but never difficult. 

## Example R Markdown Output

```{r}
plot(mtcars)
```


rmarkdown::render("C:/Users/ejwar/Desktop/awarhus.github.io/call_Rmd/2020-9-11-Programming-Background.Rmd", output_format = "github_document", output_dir ="C:/Users/ejwar/Desktop/awarhus.github.io/_posts",output_options = list(html_preview = FALSE))

C:/Users/ejwar/Desktop/awarhus.github.io/call_Rmd/2020-9-11-Programming-Background.Rmd